---
title: "Qmm_Assignment_1"
author: "Kruthi  Tatavarthy"
date: '2022-09-23'
output: html_document
---

#The Weigelt Corporation has three branch plants with excess production capacity. Fortunately, the #corporation has a new product ready to begin production, and all three plants have this capability, #so some of the excess capacity can be used in this way. This product can be made in three #sizes–large, medium, and small–that yield a net unit profit of $420, $360, and $300, respectively. #Plants 1, 2, and 3 have the excess capacity to produce 750, 900, and 450 units per day of this #product, respectively, regardless of the size or combination of sizes involved.

#The amount of available in-process storage space also imposes a limitation on the production rates of #the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000 square feet, respectively, of #in-process storage space available for a day’s production of this product. Each unit of the large, #medium, and small sizes produced per day requires 20, 15, and 12 square feet, respectively. Sales #forecasts indicate that if available, 900, 1,200, and 750 units of the large, medium, and small #sizes, respectively, would be sold per day.

#At each plant, some employees will need to be laid off unless most of the plant’s excess production #capacity can be used to produce the new product. To avoid layoffs if possible, management has decided #that the plants should use the same percentage of their excess capacity to produce the new product. #Management wishes to know how much of each of the sizes should be produced by each of the plants to #maximize profit.


#a. Define the decision variables

#The decision variables are the number of units of the new product, regardless its size, that should be produced on each plant to maximize the company’s profit.

#Note:

#$X_i$ = means the number of units produced on each plant, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3)

#L, M, and S = means the product's size, where L = large, M = medium, and S = small.

#The decision variables are:

#$X_iL$ = number of large items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

#$X_iM$ = number of medium items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

#$X_iS$ = number of small items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

#b. Formulate a linear programming model for this problem.

#Let

#$X_iL$ = number of large items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

#$X_iM$ = number of medium items produced on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

#$X_iS$ = number of small items produced on on plant $i$, where $i$= 1 (Plant 1), 2 (Plant 2), and 3 (Plant 3).

#Maximize profit

#$Z= 420 \ (X_1L + X_2L + X_3L) + 360 \ (X_1M + X_2M + X_3M) + 300 \ (X_1S + X_2S + X_3S)$
#Constraints:

#Total number of size’s units produced regardless the plant:

#$L = X_1L + X_2L + X_3L$

#$M = X_1M + X_2M + X_3M$

#$S = X_1S + X_2S + X_3S$
#Production capacity per unit by plant each day:

#Plant 1 = $X_1L + X_1M + X_1S \ 750$

#Plant 2 = $X_2L + X_2M + X_2S \ 900$

#Plant 3 = $X_3L + X_3M + X_3S \ 450$
#Storage capacity per unit by plant each day:
#Plant 1 = $20 X_1L + 15 X_1M + 12 X_1S \ 13000$

#Plant 2 = $20 X_2L + 15 X_2M + 12 X_2S \ 12000$

#Plant 3 = $20 X_3L + 15 X_3M + 12 X_3S \ 5000$

#Sales forecast per day:

#$L = X_1L + X_2L + X_3L \ 900$

#$M = X_1M + X_2M + X_3M \ 1200$

#$S = X_1S + X_2S + X_3S \ 750$
#The plants should use the same percentage of their excess capacity to produce the new product.

#$\dfrac {X_1L + X_1M + X_1S} {750}$ = $\dfrac {X_2L + X_2M + X_2S} {900}$ = $\dfrac {X_3L + X_3M + X_3S} {450}$


#It can be simplified as:
#a) $900 (X_1L + X_1M + X_1S) - 750 (X_2L + X_2M + X_2S) = 0$

#b) $450 (X_2L + X_2M + X_2S) - 900 (X_3L + X_3M + X_3S) = 0$

#c) $450 (X_1L + X_1M + X_1S) - 750 (X_3L + X_3M + X_3S) = 0$

#All values must be greater or equal to zero

#$L, M,$ and $S \ge 0$

#$X_iL, X_iM,$ and $X_iS \ge 0$

#---------------SOLUTION USING R---------------------------
```{r}
# Import the lpSolve package. 
library(lpSolve)


# Setting coefficients of the objective function assignment_objfunc
assignment_objfunc <- c(420, 420, 420,
                360, 360, 360,
                300, 300, 300)
# Setting the left hand side of the problem's constraints as assignment_leftconst
assignment_leftconst <- matrix(c(1, 1, 1, 0, 0, 0, 0, 0, 0,
                        0, 0, 0, 1, 1, 1, 0 ,0, 0,
                        0, 0, 0, 0, 0, 0, 1, 1, 1,
                        20, 15, 12, 0, 0, 0, 0, 0, 0,
                        0, 0, 0, 20, 15, 12, 0, 0, 0,
                        0, 0, 0, 0, 0, 0, 20, 15, 12,
                        1, 0, 0, 1, 0, 0, 1, 0, 0,
                        0, 1, 0, 0, 1, 0, 0, 1, 0,
                        0, 0, 1, 0, 0, 1, 0, 0, 1,
                        900, 900, 900, -750, -750, -750, 0, 0, 0,
                        0, 0, 0, 450, 450, 450, -900, -900, -900,
                        450, 450, 450, 0, 0, 0, -750, -750, -750), nrow = 12, byrow = TRUE)
# Setting the right hand side of the problem's constraints as assignment_rightconst
assignment_rightconst <- c(750,
                 900,
                 450,
                 13000,
                 12000,
                 5000,
                 900,
                 1200,
                 750,
                 0,
                 0,
                 0)


# Setting the unequality signs as assignment_uneqsigns
assignment_uneqsigns <- c("<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "<=",
              "=",
              "=",
              "=")
# Set up the final lp problem
lp("max", assignment_objfunc, assignment_leftconst, assignment_uneqsigns, assignment_rightconst)


# To get the solution of the lp problem
lp("max", assignment_objfunc, assignment_leftconst, assignment_uneqsigns, assignment_rightconst)$solution

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
